---
title: "Merging retrieved abstracts"
author: "Franz Prante"
format: html
---

## Merging ris-files which include our missing abstracts

Based on the URLs and titles from entries without complete abstracts, a student assistant collected abstracts from the websites of the bibliographic entries, where possible. 

### How to merge these completed entries with the already complete entries?

#### 1st Step - DONE

First, I prepared a dataset, that contains those entries from the initial duplicate-free dataset that are not in "entries_without_complete_abstracts.csv". I added a function to `extracting_URLs_script.R` that did this. The file was stored as `entries_complete_abstracts.csv`.

#### 2nd Step - DONE

This is already done: I imported the initial "merged_EL_GS_no_duplicates.ris" into Zotero to make Zotero know the keys. Afterwards, I imported your ris-file that you retrieved based on the 73 titles of the entries that had no URLs. We removed the remaining duplicates and entries with missing abstracts together. Then I exported this file to the GitHub repo as `abstracts_from_titles.ris` and `abstracts_from_titles.csv`.

#### 3rd Step - DONE

You need to import the initial "merged_EL_GS_no_duplicates.ris" into Zotero to make Zotero know the keys. Afterwards, create an empty new collection in Zotero. Now import the ris-files of the student assistant from the Nextcloud, one by one, and move them as a subcollection into the empty collection (drag and drop). Do this with all the ris-files.
You will now have a very large amount of duplicates. But don't remove duplicates for now. First, delete the "merged_EL_GS_no_duplicates" collection (with items!) from Zotero. This procedure should ensure that Zotero would have resolved any "Key" conflicts between the original dataset and the ris-files from the student assistant. You can now remove any duplicates (which should be a lot less then before, now it is only the duplicates between the ris-files from the student assistant).

Afterwards, export the total collection of now duplicate-free student ris-files (in Zotero, you have to click on the collection and then select all items and right click on them to export everything). Make sure to export both a `ris` and a `csv` version of this dataset for data sharing on GitHub. Name the files `abstracts_from_URLs.ris` and `abstracts_from_URLs.csv`. 

You can already store this on GitHub in the folder "retrieving missing or incomplete abstracts" but please work in this branch on - it is important that we both double check everything before merging into main. When you are done, you can create a pull request and select me as a reviewer. 

#### 4th Step - In R

Merge the three files:

1. `entries_complete_abstracts.csv`
2. `abstracts_from_titles.csv`
3. `abstracts_from_URLs.csv`

This code should do it:
```{r}
library(tidyverse)
library(here)

filepath1 <- here::here("data/study search/database search/processed/preparation for abstract screening/retrieving missing or incomplete abstracts/entries_complete_abstracts.csv")
filepath2 <- here::here("data/study search/database search/processed/preparation for abstract screening/retrieving missing or incomplete abstracts/abstracts_from_titles.csv")
filepath3 <- here::here("data/study search/database search/processed/preparation for abstract screening/retrieving missing or incomplete abstracts/abstracts_from_URLs.csv")
df1 <- readr::read_csv(filepath1)
df2 <- readr::read_csv(filepath2)
df3 <- readr::read_csv(filepath3)

df <- rbind(df1, df2, df3)
```

## Final checks 

Do a final round of checks:
```{r}
sum(is.na(df$`Abstract Note`)) # Should be 0. Otherwise, there are still completely missing abstracts.
sum(grepl("…", df$`Abstract Note`) == TRUE) # Should be 0. Otherwise there are still shortened Google Scholar abstracts in the dataframe.
```

Final duplicate check (same title & same abstract)
```{r}
duplicated_rows <- duplicated(df[,c("Title", "Abstract Note")]) | duplicated(df[,c("Title", "Abstract Note")], fromLast = TRUE)
sum(duplicated_rows) # Number of seeming duplicates based on title and abstract
View(df[duplicated_rows, ])
```
We should discuss what to do with the remaining duplicates based on how many there are (having a few duplicates should cause no worry for ASReview, but a lot may).

Based on these final checks, maybe do another round of duplicates removal and abstract retrieval, if this seems promising. Then repeat the final checks.

## Store the dataset as `full_sample_unlabeled.csv`
```{r}
df_final <- # Define the final dataframe, depending on what we did with the remaining duplicates and missing abstracts.
final_filepath <- ... # Let's discuss were we should best store this. This is important, as from this file, we will start the abstract screening.
write.csv(df_final, final_filepath, row.names = FALSE)

```





















